\documentclass{article}

\usepackage{cancel}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

	\section*{Exercises for Chapter 1}
	
	\begin{enumerate}
		\item Let $A$ be the set $\{ \alpha , \{ 1, \alpha \}, \{ 3 \}, \{\{ 1, 3 \} \}, 3 \}$. Which of the following
		statements are true or false?
		
		\begin{enumerate}
			\item $\alpha \in A$
			
				True
				
			\item $\{ \alpha \} \in A$
			
				False
				
			\item $\{ 1, \alpha \} \subseteq A$ 
			
				False
				
			\item $\{ 3, \{3\} \} \subseteq A$
			
				True
				
			\item $\{ 1, 3 \} \in A$
			
				True
				
			\item $\{\{1, 3\} \} \subseteq A$
			
				False
				
			\item $\{\{1, \alpha \}\} \subseteq A$
			
				True
				
			\item $\{1, \alpha \} \cancel{ \in } A$
			
				False
				
			\item $\emptyset \subseteq A$
			
				True
		\end{enumerate}
		
		\item Let $B, C, D, E$ be the following sets:
		
			$$B  = \{x | x \text{ a real number}, x^2 < 4 \} ,$$
			$$C = \{x | x \text{ a real number}, 0 \leq x < 2 \},$$
			$$D = \{x | x \in \mathbb{Z}, x^2 < 1 \}. $$
			$$E = \{ 1 \}$$
			
		\begin{enumerate}
		
			\item Which pair of these sets has the propery that neither is contained in the other?
			
				Set $B$ is the same as $-2 < x < 2$. $B$ and $C$ contain common real numbers. 
				$D$ is equal to $-1 < x < 1$. $D$ and $E$ is the pair of sets that neither is contained
				in the other.
				
			\item You are given that $X$ is one of the sets $B, C,  D, E,$ but do not know which one.
				You are also given that $E \subseteq  X$ and $X \subseteq B$. What can you deduce
				about $X$?
				
				Because $E \subseteq X$ we know $1 \in X$. We can deduce from this that $X \cancel{=} D$ as
				$1 \cancel{\in} D$. If $X \subseteq B$ then $X$ could be $B$ or $C$ as ( as $C \subseteq B$) or
				$E$ ( as $E \subseteq B$).
		\end{enumerate}
		
		\item Which of the following arguments are valid? For the valid ones, write down the argument symbolically.
		
		\begin{enumerate}
		
			\item I eat chocolate if I am depressed. I am not depressed. Therefore I am not eating chocolate.
			
				This argument is not valid. The lack of depression says nothing about the eating of chocolate.
				The subject may be eating chocolate when not depressed.
				
			\item I eat chocolate only if I am depressed. I am not depressed. Therefore I am not eating chocolate.
			
				This argument is valid. If $E$ is ``I am eat chocolate'' and $D$ is ``I am depressed'' then 
				``I eat chocolate only if I am depressed'' is represented as $E \Rightarrow D$. If $E \Rightarrow D$
				is true then $\neg D \Rightarrow \neg E$ is also true so the argument is valid.
				
			\item If a movie is worth seeing, then it was not made in England. A movie is worth seeing only if critic
				Ivor Smallbrain reviews it. The movie \emph{The Good, the Bad and the Mathematician} was not
				reviewed by Ivor Smallbrain. Therefore \emph{The Good, the Bad and the Mathematician} was not
				not made in England.
				
				$S$ is `` worth seeing''. $E$ is ``made in England'' and $R$ is ``reviewed by Ivor Smallbrain''.
				
				$$\neg S \Rightarrow \neg E$$
				$$S \Rightarrow R$$
				
				$S \Rightarrow R$ means $\neg R \Rightarrow \neg S$ must be true. So if $\neg R$ is true then $\neg S$
				and so $\neg E$.
		\end{enumerate}
		
		\item $A$ and $B$ are two statements. Which of the following statements about $A$ and $B$ implies one or
			more of the other statements?
			
			\begin{enumerate}
				\item Either $A$ or $B$ is true.
				
				\item $A \Rightarrow B$.
				
				\item $B \Rightarrow A$.
				
				\item $\neg A \Rightarrow B$.
				
				\item $\neg B \Rightarrow A$.
			\end{enumerate}
			
			Statement (a) implies statements (d) and (e).
			
		\item Which of the following statements are true, and which are false?
	
		\begin{enumerate}
		
			\item $n = 3 \text{ only if } n^2 - 2n - 3 = 0$
			
				This is true. $n = 3 \Rightarrow n^2 - 2n - 3 = 0$
				
			\item $n^2 - 2n - 3 = 0 \text{ only if } n = 3$
			
				This is false. $n^2 - 2n - 3 = (n - 3)(n + 1)$ so $n$ could equal $-1$.
				
			\item $n^2 -2n -3 = 0 \text{ then } n =3$
			
				This is false for the same reasons as above.
				
			\item For integers $a$ and $b$, $ab$ is a square only if both $a$ and $b$ are squares.
			
				This is false. 144 is the square of 12. 3 and 48 are integer factors of 144. Neither 3 or 48 are squares.
				
			\item For integers $a$ and $b$, $ab$ is a square if both $a$ and $b$ are squares.
			
				This is true.
				
				$$a = k_{1}^2, b = k_{2}^{2}$$
				$$ab =  k_{1}^{2} k_{2}^{2}$$
				
				$$\text{So } ab = (k_1 k_2)^2$$
				
			
		\end{enumerate}	
		
		\item Write down careful proofs of the following statemens:
		
		\begin{enumerate}
		
			\item $\sqrt{6} - \sqrt{2} > 1$.
			
			We need to construct a proof by contradiction.
			
			$$\sqrt{6} - \sqrt{2} \leq 1$$
			$$(\sqrt{6} - \sqrt{2})^2 \leq (1)^2$$
			$$6 - 2\sqrt{2}\sqrt{6} + 2 \leq 1$$
			$$8 - 2\sqrt{12} \leq 1$$
			$$-2\sqrt{12} \leq -7$$
			$$(-2\sqrt{12})^2 > (-7)^2$$
			$$48 > 49$$
			
			\item If $n$ is an integer such that $n^2$ is even, then $n$ is even.
			
			Suppose $n$ is odd.
			
			$$n^2 = (2k)^2$$
			$$n^2 = 4k^2 = 2(2k^2)$$
			
			So $n^2$ is even.
			
			\item If $n = m^3 - m$ for some integer $m$, then $n$ is multiple of 6.
			
				$$m^3 - m = (m-1)m(m+1)$$
				
				This factors into three consecutive integers. Because every second integer is 
				a factor of 2 and every third integer is a factor of 3, (m-1)m(m+1) is a multiple of 6.
				
				
		\end{enumerate}
		
		\item Disprove the following statements:
		
		\begin{enumerate}
		
			\item If $n$ and $k$ are positive integers, then $n^k - n$ is always divisible by $k$.
			
				A counterexample.
			
				$(5^6 - 5)/5 = 2603.3333 ...$
				
			\item Every positive integer is the sum of three squares (the squares being 0, 1, 4, 9, 16, etc.).
			
				If we take $4 + 1 + 1 = 6$ and add 1 to get 7, 7 is not a sum of squares.
		\end{enumerate}
		
		\item Given that the number 8881 is not a prime number, prove that it has a prime factor that is at most 89.
			\emph{(Hint: Don't try to factorize 8881! Try to be a bit clever and prove it by contradiction.)}
			
			$$\sqrt{8881} = 94.239....$$
			
			So 8881 has a set of factors $k | k \leq 94$.
			
			Let's assume 8881 does not have any prime factors less than 89, then 8881 must have prime factors
			between 90 and 94. None of 90, 91, 92, 93 or 94 are factors of 8881. If 8881 has no factors above 
			89 and it is not a prime number then if must have a prime factor that is at most 89.
			
		\item In this question I am assuming you know what a prime number is; if not, take a look at the last section
		of Chapter 8.
		
		For each of the following statements, form its negation and either prove that the statement is true or prove
		that its negation is true:
		
		\begin{enumerate}
			\item $\forall n \in \mathbb{Z}$ such that $n$ is a prime number, $n$ is odd
			
			The negation of this is
			
			$$\exists n \in \mathbb{Z} \text{ such that } n \text{ is a real number }, n \text{ is even.}$$
			
			The negation is true as $n = 2$ is an even prime number.
			
			\item $\forall n \in \mathbb{Z}, \exists a, b, c, d, e, f, g, h \in \mathbb{Z}$ such that
			
				$$n = a^3 + b^3 + c^3 + d^3 + e^3 + f^3 + g^3 + h^3$$
				
			The negation of this is
			
				$\exists n \in \mathbb{Z}, \forall a, b, c, d, e, f, g, h \in \mathbb{Z}$ such that
				
				$$n \cancel{ = }  a^3 + b^3 + c^3 + d^3 + e^3 + f^3 + g^3 + h^3$$
				
			\item $\exists x \in \mathbb{Z} \text{ such that } \forall n \in \mathbb{Z}, x \cancel{ = } n^2 +2$
			
				The negation of this is $\forall x \in \mathbb{Z} \text{ such that } \exists n \in \mathbb{Z}, x = n^2 + 2$
				
				The negation is false as $n = -1$ does not equal any $n^2 + 2$. So the original statement is true.
			
				
		\end{enumerate}
	
	\end{enumerate}
	

	

\end{document}